### 2016-11-11 paper.tex
esann style

\documentclass{esannV2}
\usepackage{subfig}
\usepackage{color}
\usepackage{url}

%***********************************************************************
% !!!! IMPORTANT NOTICE ON TEXT MARGINS !!!!!
%***********************************************************************
%
% Please avoid using DVI2PDF or PS2PDF converters: some undesired
% shifting/scaling may occur when using these programs
% It is strongly recommended to use the DVIPS converters, and to submit
% PS file. You may submit a PDF file if and only if you use ADOBE ACROBAT
% to convert your PS file to PDF.
%
% Check that you have set the paper size to A4 (and NOT to letter) in your
% dvi2ps converter, in Adobe Acrobat if you use it, and in any printer driver
% that you could use.  You also have to disable the 'scale to fit paper' option
% of your printer driver.
%
% In any case, please check carefully that the final size of the top and
% bottom margins is 5.2 cm and of the left and right margins is 4.4 cm.
% It is your responsibility to verify this important requirement.  If these margin requirements and not fulfilled at the end of your file generation process, please use the following commands to correct them.  Otherwise, please do not modify these commands.
%
\voffset 0 cm \hoffset 0 cm \addtolength{\textwidth}{0cm}
\addtolength{\textheight}{0cm}\addtolength{\leftmargin}{0cm}

%***********************************************************************
% !!!! USE OF THE esannV2 LaTeX STYLE FILE !!!!!
%***********************************************************************
%
% Some commands are inserted in the following .tex example file.  Therefore to
% set up your ESANN submission, please use this file and modify it to insert
% your text, rather than staring from a blank .tex file.  In this way, you will
% have the commands inserted in the right place.

\begin{document}
%style file for ESANN manuscripts
\title{Title}

%***********************************************************************
% AUTHORS INFORMATION AREA
%***********************************************************************
%\author{First author$^1$ and Second author$^2$
\author{A$^1$, B$^2$ and C$^3$
%
% Optional short acknowledgment: remove next line if non-needed
%\thanks{This is an optional funding source acknowledgement.}
%
% DO NOT MODIFY THE FOLLOWING '\vspace' ARGUMENT
\vspace{.3cm}\\
%
% Addresses and institutions (remove "1- " in case of a single institution)
1- Department of Mathematics, University of Padova\\
via Trieste 63, Padova, Italy
\vspace{.1cm}\\
2- Computational Statistics and Machine Learning (CSML) \\
Istituto Italiano di Tecnologia, Via Morego 30, Genova, Italy
\vspace{.1cm}\\
3- ... \\
...
}

%commento sta roba
%1- School of First Author - Dept of First Author \\
%Address of First Author's school - Country of First Author's
%school
%
% Remove the next three lines in case of a single institution
%\vspace{.1cm}\\
%2- School of Second Author - Dept of Second Author \\
%Address of Second Author's school - Country of Second Author's school\\
%}
%***********************************************************************
% END OF AUTHORS INFORMATION AREA
%***********************************************************************

\maketitle

%\renewcommand{\baselinestretch}{.95}

\begin{abstract}
...
\end{abstract}

\section{Introduction}
...

% ****************************************************************************
% BIBLIOGRAPHY AREA
% ****************************************************************************

\begin{footnotesize}

% IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
% ----------------------------------------------------------------------------

% ----------------------------------------------------------------------------

% IF YOU USE BIBTEX,
% - DELETE THE TEXT BETWEEN THE TWO ABOVE DASHED LINES
% - UNCOMMENT THE NEXT TWO LINES AND REPLACE 'Name_Of_Your_BibFile'

\bibliographystyle{unsrt}
\bibliography{biblio.bib}

\end{footnotesize}

% ****************************************************************************
% END OF BIBLIOGRAPHY AREA
% ****************************************************************************

\end{document}

### 2016-11-16 paper.tex
first structure
structure
Pre-alpha version of kernels for structures. TO CHECK, but I'll do it tomorrow.

@@
 \section{Introduction}
+In different real-world domains, it may be easy to encode examples in a structured form.
+For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds.
+Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are liked.
+In these cases, specific machine learning techniques have to be adopted.
+Kernel methods are one option, where it suffices to adopt a kernel function defined for the kind of data under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.
+
+With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand. The values of these hyper-parameters can strongly affect the predictive performance of the method.
+Usually, these parameters are:
+\begin{enumerate}
+ \item the choice of the kernel to adopt;
+ \item the hyper-parameters of the selected kernel;
+ \item the hyper-parameters of the learning algorithm.
+\end{enumerate}
+One commonly adopted and simple approach to fix these parameters is to fix a-priori some possible values for each parameter, and to test each possible combination on a validation set.
+This approach is commonly referred to as grid-search (from the parameter grid).
+Then, only the best combination is used to predict the test set, in order to produce an unbiased error estimation of the method (if necessary).
+In particular, for each point in the grid, a learning procedure have to be computed.
+In the case of kernel algorithms, a different kernel matrix has to be computed for the hyper-parameters at points 1 and 2.
+This procedure may be very time consuming.
+A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
+In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
+\section{Kernel for structures and Multiple Kernel Learning}
+When dealing with structured data, the choice of the kernel to adopt is a key step.
+Depending on the type of data under consideration, different proposals are available in literature, each one with a different tradeoff between predictive performance and computational time (of course, this tradeoff depends from the considered task).
+In this paper we focus on graphs, i.e. we consider each example to be a different graph.
+In this case, there are several graph kernels defined in literature based on random walks, shortest paths or subgraphs up to a fixed size[TODO].
+The problem with these kernels is the high computational complexity, that makes them unapplicable to several real-world datasets.
+Recently, different almost linear time graph kernels have been defined in literature, and these are the ones we focus o in this paper.
+In the following we will give some details about the considered alternatives.
+\textcolor{red}{TODO}\\
+\begin{itemize}
+ \item WL
+ \item NSPDK
+ \item ODD$_{ST}$
+\end{itemize}
+
+...
+
+\section{Our framework}
+...
+
+\section{Experimental Results}
+...
+
+\section{Conclusion}
 ...

### 2016-11-17 paper.tex
Typos correction

@@
 When dealing with structured data, the choice of the kernel to adopt is a key step.
-Depending on the type of data under consideration, different proposals are available in literature, each one with a different tradeoff between predictive performance and computational time (of course, this tradeoff depends from the considered task).
+Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
 In this case, there are several graph kernels defined in literature based on random walks, shortest paths or subgraphs up to a fixed size[TODO].
-The problem with these kernels is the high computational complexity, that makes them unapplicable to several real-world datasets.
+The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
 Recently, different almost linear time graph kernels have been defined in literature, and these are the ones we focus o in this paper.

### 2016-11-17 paper.tex
MKL and EasyMKL (first version)

@@
 \usepackage{url}
+
+% My packages
+\usepackage{ctable} % for \specialrule command
+%\usepackage{tikz}
+%\usepackage{pgfplots}
+%\usepackage{filecontents}
+%\usepackage{amsfonts}
+%\usepackage{booktabs}
+%\usepackage{amsthm}
+\usepackage{amssymb,amsmath,array}
+%\usepackage{color}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
+%\usepackage{multirow}
+%\usepackage{array}
+%\usepackage{subfig}
+%\usepackage{caption}
+%\usepackage{graphicx}
+%\usepackage{hyperref}
+%\usepackage{algorithmicx}
+%\usepackage{float}
+%\usepackage{soul}
+%\usepackage{amsfonts}
+%\usepackage{subfigure}
+\usepackage{amsbsy}
+%\usepackage{setspace}
+%\usepackage{hyperref}
+%\usepackage[bookmarks=false]{hyperref}
+%\usepackage{babel,blindtext}
+\usepackage{color}
+
+% My commands
+\newcommand{\Real}{\mathbb{R}}
+\newcommand{\Natu}{\mathbb{N}}
+\newcommand{\dd}{{\bf d}}
+\newcommand{\xx}{{\bf x}}
+\newcommand{\yy}{{\bf y}}
+\newcommand{\zz}{{\bf z}}
+\newcommand{\ff}{{\bf f}}
+\newcommand{\ww}{{\bf w}}
+\newcommand{\vv}{{\bf v}}
+\newcommand{\AAA}{{\bf A}}
+\newcommand{\CC}{{\bf C}}
+\newcommand{\DD}{{\bf D}}
+\newcommand{\EE}{{\bf E}}
+\newcommand{\GG}{{\bf G}}
+\newcommand{\KK}{{\bf K}}
+\newcommand{\YY}{{\bf Y}}
+\newcommand{\MM}{{\bf M}}
+\newcommand{\HH}{{\bf H}}
+\newcommand{\II}{{\bf I}}
+\newcommand{\XX}{{\bf X}}
+%\newcommand{\NN}{{\bf N}}
+\newcommand{\cU}{{\cal U}}
+\newcommand{\cI}{{\cal I}}
+\newcommand{\cR}{{\cal R}}
+\newcommand{\cN}{{\cal N}}
+\newcommand{\cQ}{{\mathcal Q}}
+\newcommand{\1}{{\bf 1}}
+\newcommand{\Exp}{\mathbb{E}}
+\newcommand{\labelfun}{L}
+\newcommand{\node}{v}
+\newcommand{\cK}{{\cal K}}
+%\newtheorem{lemma}{Lemma}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{corollary}{Corollary}
+%\newtheorem{proposition}{Proposition}
+%\newtheorem{definition}{Definition}
+%\newtheorem{remark}{Remark}
+\newcommand{\cC}{{\cal C}}
+\newcommand{\R}{{\mathbb R}}
+\newcommand{\N}{{\mathbb N}}
+\newcommand{\ggamma}{\pmb{\gamma}}
+\newcommand{\aalpha}{\pmb{\alpha}}
+\newcommand{\bbeta}{\pmb{\beta}}
+\newcommand{\eeta}{\pmb{\eta}}
+\newcommand{\ssigma}{\pmb{\sigma}}
+\newcommand{\llambda}{\pmb{\lambda}}
+\newcommand{\mmu}{\pmb{\mu}}
+\newcommand{\pphi}{\pmb{\phi}}
 
@@
 In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
+
 \section{Kernel for structures and Multiple Kernel Learning}
@@
 
-...
+\subsection{Multiple Kernel Learning (MKL)}
+\label{MKL}
+MKL \cite{Bach2004,Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
+The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
+$
+	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
+$
+with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space.
+The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
+
+Using this formulation, we are studying the family of sums of kernels in the feature space.
+It is well know that the sum of two kernels can be seen as the concatenation of the features contained in both the RKHS \cite{Shawe-Taylor2004}.
+Extending the same idea, the weighted sum of a list of basic kernels can be seen as a weighted concatenation of all the features contained in all the RKHS (where the weights are the square roots of the learned weights $\eta_k$).
+
+ %structured sparsity regularizers \cite{Micchelli2010,Micchelli2013}.
+The problem of searching for a combinations of basic kernels can be rephrased as a regularization problem in which the prediction function is the sum of functions $f_r$ in the RKHS of kernel $\KK_r$ and the regularization term is the combination of the norms of the $f_r$ in the associated RKHS \cite{Micchelli2005a}.
+%,Micchelli2007
+For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.
+
+These algorithms are supported by several theoretical results that bound the \emph{estimation error} (i.e.
+the difference between the true error and the empirical margin error).
+These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Srebro2006,Cortes2009c,Hussain2011,Hussain2011a}.
+%,Kakade2009,Micchelli2005,Kloft2012
+
+Existing MKL approaches can be divided in two main categories.
+In the first category, \emph{Fixed or Heuristic}, some fixed rule is applied to obtain the combination.
+They usually get results scalable with respect to the number of kernels combined but their effectiveness critically depends on the domain at hand.
+They use a parameterized combination function and find the parameters of this function generally by looking at some measure obtained from each kernel separately,  often giving a suboptimal solution (since no information sharing among the kernels is exploited).
+
+On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine (e.g.
+structural risk based target function) or formulated as a different model (e.g.
+alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Bach2004,Varma2009}.
+%,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010
+
+%*** good refs. [F. R. Bach, R. Jenatton, J. Mairal, and G. Obozinski. Optimization with sparsity-inducing penalties. Foundations and Trends in Machine Learning, 4:1?106, 2011.] \cite{Bach2012} ***
+
+\subsubsection{EasyMKL}
+\label{EasyMKL}
+EasyMKL \cite{Aiolli2015} is a recent MKL algorithm able to combine sets of basic kernels by solving a simple quadratic optimization problem.
+Besides its proved empirical effectiveness, a clear advantage of EasyMKL compared to other MKL methods is its high scalability with respect to the number of kernels to be combined.
+Specifically, its computational complexity is constant in memory and linear in time.
+
+EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples.
+In particular, the general problem EasyMKL tries to optimize is the following:
+\vspace{-0.4cm}
+\begin{equation}
+\label{eq:easymklotig}
+\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \lambda ||\boldsymbol{\gamma}||^2.
+\end{equation}
+\vspace{-0.3cm}
+
+where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\lambda$ is a regularization hyper-parameter.
+The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
+$
+Note that any element $\boldsymbol{\gamma} \in \Gamma$ corresponds to a pair of points, the first in the convex hull of positive training examples and the second in the convex hull of negative training examples.
+At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
+
+The objective function in Eq.
+\ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
+This equation is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}.
+The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation.
+Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$).
+From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
+\begin{equation}
+\label{eq:easyeta}
+	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
+\end{equation}
+
+In the following sections, we will refer to this algorithm as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
+%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyper-parameter $\Lambda$.
 
@@
 \bibliographystyle{unsrt}
-\bibliography{biblio.bib}
+\bibliography{donini,biblio}
 

### 2016-11-23 paper.tex
Typos
ivanolauriola@gmail.com

@@
 \newcommand{\pphi}{\pmb{\phi}}
+\newcommand{\res}[2]{$#1_{\pm#2}$}
 
@@
 
-\section{Our framework}
-...
+\section{Our framework (devo finire di sistemare)}
+In several problems solved using MKL paradigm, the number of kernels used can be very high and, when we use structured data as input, such as graph, the computational effort to calculare each of them can be expensive.
+Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
 
-\section{Experimental Results}
-...
+In order to avoid this problem, we propose a method to reduce the number of kernel matrices calculated, based on the robustness of weights vector $\eta$ over the number of training samples used.\\
+In particular if $\eta$, learned using the whole set of data, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
+In this way we can learn quickly the kernels combination, but we have to calculate each of them anyway.
+We want to take a step forward by using $\eta_s$ to perform a kernels selection, aiming to build the complete model using only the top kernels.\\
+The top kernels are those with the best margin-contribution defined in $\eta_s$.
+
+In the second phase, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
+The kernels discarded can be considered as noise and irrelevant in combination, so their elimination [???].
+In this way we calculate all kernels using a subset of data, and a subset of kernels using the whole training data.
+
+\section{Experimental Results (devo finire di sistemare)}
+Firstly, we performed some experiment to check the base of our method. In particular we want to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
+\figurename\ \ref{fig:weights} shows the weights vector obtained by EasyMKL with different number of training samples.
+
+\begin{figure}[ħtb]
+\includegraphics[width=\textwidth]{img/weights_GDD.png}
+\caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the difference with the weights vector calculated on all data. }
+\label{weights}
+\end{figure}
+
+However, in this context, two weights vectors are similar if the top kernels are the same. The exact (rescaled eventually) values are useless, we have to chose the same kernels using a subset of data.
+The similarity metric used for comparison is the jaccard similarity score.
+\figurename\ \ref{fig:jaccard} shows the jaccard score by considering different percentage of top kernels and different number of training data used.
+
+\begin{figure}[htb]
+\centering
+\subfloat[a]{\includegraphics[width=0.42\textwidth]{img/CPDB_jaccard.png}}
+\subfloat[b]{\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}}
+\caption{Average jaccard values between the indices of top kernels using a subset of training data and using the whole set.}
+\label{fig:jaccard}
+\end{figure}
+
+The datasets used in our experiments are: [???]
+
+In the first step of our method, we learn the weights vector $\eta_{10}$ using a subset $(10\%)$ of training data and the whole set of kernels.
+To do this, we perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner.
+The hyperparameters are $(\lambda,C)$.
+We chose the top $10\%$ kernels using the weights vector with the best result in the cv procedure.\\
+In the latter step we calculate the complete matrix relative to the top kernels selected and use these kernels to fit the model. In particular we divided our approach in 3 sub-methods:
+\begin{itemize}
+\item{}use the EasyMKL algorithm to re-clculate the kernel with top kernels;
+\item{}calculate the resulting kernel as the average;
+\item{}use the same weights (rescaled) from the first learning step.
+\end{itemize}
+For testing, we compared our method with 3 hard baselines, that are:
+\begin{itemize}
+\item{}validation: we calculate all kernel matrices and select which has the best results in validation;
+\item{}average: we calculate the kernel as the average of all base kernels;
+\item{}combined: we use EasyMKL to combine the whole set of kernels;
+\end{itemize}
+In all baselined and in the latter training step of each proposed methods, we use a stratified nested 10-fold cross-validation to chose the best hyperparameters sets, that are $\lambda$ for models where we use EasyMKL and $C$ for all baselines and methods since we always use a SVM as base learner.
+
+\subsection{Results}
+[...]
+\begin{table}[]
+\centering
+\caption{My caption}
+\label{my-label}
+\resizebox{\textwidth}{!}{
+\begin{tabular}{l|c|lll|lll}
+\hline
+dataset & \# train & validation      & all (easy) & all (average) & subset\_easy & subset\_aver & subset\_w \\
+\hline
+CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $0.8850_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
+\\
+MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{0.9331}{0.053}    \\
+\\
+CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.11} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+\\
+GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.869}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+\\
+AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+\\
+NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{0.8851}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+\\
+NCI109 & 4127 & \res{0.8728}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+\\
+\hline
+\end{tabular}}
+\end{table}
 

### 2016-11-23 paper.tex
IMG folder
Modified introduction and started graph kernels section

@@
 For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds.
-Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are liked.
+Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
 In these cases, specific machine learning techniques have to be adopted.
@@
 
-With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand. The values of these hyper-parameters can strongly affect the predictive performance of the method.
-Usually, these parameters are:
-\begin{enumerate}
- \item the choice of the kernel to adopt;
- \item the hyper-parameters of the selected kernel;
- \item the hyper-parameters of the learning algorithm.
-\end{enumerate}
-One commonly adopted and simple approach to fix these parameters is to fix a-priori some possible values for each parameter, and to test each possible combination on a validation set.
-This approach is commonly referred to as grid-search (from the parameter grid).
-Then, only the best combination is used to predict the test set, in order to produce an unbiased error estimation of the method (if necessary).
-In particular, for each point in the grid, a learning procedure have to be computed.
-In the case of kernel algorithms, a different kernel matrix has to be computed for the hyper-parameters at points 1 and 2.
-This procedure may be very time consuming.
+With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand.
+The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
+Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii)the hyper-parameters of the learning algorithm.
+A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these paraeters are referres to as \textit{parameters grid}).
+Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
+
+The learning algorithm has to be trained for each hyper-parameter combination, and this procedure may be very time consuming.
 A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
+In the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of their hyper-parameters combination.
+This step can also be time consuming, especially when dealing with data in a structured form.
 In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
 
-\section{Kernel for structures and Multiple Kernel Learning}
+%\section{Kernel for structures and Multiple Kernel Learning}
+\section{Backgroung}
 When dealing with structured data, the choice of the kernel to adopt is a key step.
@@
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-In this case, there are several graph kernels defined in literature based on random walks, shortest paths or subgraphs up to a fixed size[TODO].
+In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\citep{Shervashidze2009} .
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature, and these are the ones we focus o in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \citep{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
 In the following we will give some details about the considered alternatives.
@@
 
-\begin{figure}[ħtb]
+\begin{figure}[htb]
 \includegraphics[width=\textwidth]{img/weights_GDD.png}

### 2016-11-24 paper.tex
Added biblio and corrected typos

@@
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\citep{Shervashidze2009} .
+In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\cite{Shervashidze2009} .
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \citep{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
 In the following we will give some details about the considered alternatives.
@@
 \bibliographystyle{unsrt}
-\bibliography{donini,biblio}
+\bibliography{donini,biblio, Mendeley}
 

### 2016-11-24 paper.tex
Modified biblio

--- 2016-11-23 paper.tex
@@
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\citep{Shervashidze2009} .
+In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\cite{Shervashidze2009} .
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \citep{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
 In the following we will give some details about the considered alternatives.
@@
 \bibliographystyle{unsrt}
-\bibliography{donini,biblio}
+\bibliography{donini,biblio,Mendeley}
 

### 2016-11-24 paper.tex
ivano

--- 2016-11-23 paper.tex
@@
 For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds.
-Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
+Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are liked.
 In these cases, specific machine learning techniques have to be adopted.
@@
 
-With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand.
-The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
-Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii)the hyper-parameters of the learning algorithm.
-A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these paraeters are referres to as \textit{parameters grid}).
-Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
-
-The learning algorithm has to be trained for each hyper-parameter combination, and this procedure may be very time consuming.
+With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand. The values of these hyper-parameters can strongly affect the predictive performance of the method.
+Usually, these parameters are:
+\begin{enumerate}
+ \item the choice of the kernel to adopt;
+ \item the hyper-parameters of the selected kernel;
+ \item the hyper-parameters of the learning algorithm.
+\end{enumerate}
+One commonly adopted and simple approach to fix these parameters is to fix a-priori some possible values for each parameter, and to test each possible combination on a validation set.
+This approach is commonly referred to as grid-search (from the parameter grid).
+Then, only the best combination is used to predict the test set, in order to produce an unbiased error estimation of the method (if necessary).
+In particular, for each point in the grid, a learning procedure have to be computed.
+In the case of kernel algorithms, a different kernel matrix has to be computed for the hyper-parameters at points 1 and 2.
+This procedure may be very time consuming.
 A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
-In the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of their hyper-parameters combination.
-This step can also be time consuming, especially when dealing with data in a structured form.
 In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
 
-%\section{Kernel for structures and Multiple Kernel Learning}
-\section{Backgroung}
+\section{Kernel for structures and Multiple Kernel Learning}
 When dealing with structured data, the choice of the kernel to adopt is a key step.
@@
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\citep{Shervashidze2009} .
+In this case, there are several graph kernels defined in literature based on random walks, shortest paths or subgraphs up to a fixed size[TODO].
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \citep{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
+Recently, different almost linear time graph kernels have been defined in literature, and these are the ones we focus o in this paper.
 In the following we will give some details about the considered alternatives.
@@
 
-\section{Our framework (devo finire di sistemare)}
-In several problems solved using MKL paradigm, the number of kernels used can be very high and, when we use structured data as input, such as graph, the computational effort to calculare each of them can be expensive.
+\section{Our framework}
+Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be expensive.
 Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
+In order to avoid this problem, we propose a method to reduce the number of kernels, based on the robustness of combination vector $\eta$.\\
+In particular if $\eta$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
+In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
+Furthermore, we can use values in $\eta_s$ to perform a ranking over kernels, removing those below a threshold.
+Then we fit the model using only the top kernels selected.
 
-In order to avoid this problem, we propose a method to reduce the number of kernel matrices calculated, based on the robustness of weights vector $\eta$ over the number of training samples used.\\
-In particular if $\eta$, learned using the whole set of data, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
-In this way we can learn quickly the kernels combination, but we have to calculate each of them anyway.
-We want to take a step forward by using $\eta_s$ to perform a kernels selection, aiming to build the complete model using only the top kernels.\\
-The top kernels are those with the best margin-contribution defined in $\eta_s$.
+In summary, in the first phase we chose the top kernels using a subset of data, in the latter, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
 
-In the second phase, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
-The kernels discarded can be considered as noise and irrelevant in combination, so their elimination [???].
-In this way we calculate all kernels using a subset of data, and a subset of kernels using the whole training data.
+\section{Experimental Results (settings?)}
+Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
+The metric used for comparison is the jaccard similarity score. Indeed, in our context two weights vectors are similar is they provide the same top kernels.
+These experiments are summarized in \figurename\ \ref{fig:weights} and \ref{fig:jaccard}.
 
-\section{Experimental Results (devo finire di sistemare)}
-Firstly, we performed some experiment to check the base of our method. In particular we want to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
-\figurename\ \ref{fig:weights} shows the weights vector obtained by EasyMKL with different number of training samples.
-
-\begin{figure}[htb]
+\begin{figure}[!htb]
+\centering
 \includegraphics[width=\textwidth]{img/weights_GDD.png}
-\caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the difference with the weights vector calculated on all data. }
-\label{weights}
+\caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
+\label{fig:weights}
 \end{figure}
 
-However, in this context, two weights vectors are similar if the top kernels are the same. The exact (rescaled eventually) values are useless, we have to chose the same kernels using a subset of data.
-The similarity metric used for comparison is the jaccard similarity score.
-\figurename\ \ref{fig:jaccard} shows the jaccard score by considering different percentage of top kernels and different number of training data used.
-
-\begin{figure}[htb]
+\begin{figure}[!htb]
 \centering
@@
 \subfloat[b]{\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}}
-\caption{Average jaccard values between the indices of top kernels using a subset of training data and using the whole set.}
+\caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
 \label{fig:jaccard}
 \end{figure}
-
-The datasets used in our experiments are: [???]
 
@@
 The hyperparameters are $(\lambda,C)$.
-We chose the top $10\%$ kernels using the weights vector with the best result in the cv procedure.\\
-In the latter step we calculate the complete matrix relative to the top kernels selected and use these kernels to fit the model. In particular we divided our approach in 3 sub-methods:
+Then we fit the model with the best combination and chose the top $10\%$ kernels.\\
+In the latter step we calculate the top kernel matrices and combine it to get the kernel. We propose three methods to perform this combination:
 \begin{itemize}
-\item{}use the EasyMKL algorithm to re-clculate the kernel with top kernels;
-\item{}calculate the resulting kernel as the average;
+\item{}use the EasyMKL algorithm;
+\item{}calculate the average of kernels;
 \item{}use the same weights (rescaled) from the first learning step.
@@
 \begin{itemize}
-\item{}validation: we calculate all kernel matrices and select which has the best results in validation;
+\item{}validation: we select the kernel which has the best result in validation;
 \item{}average: we calculate the kernel as the average of all base kernels;
@@
 \end{itemize}
-In all baselined and in the latter training step of each proposed methods, we use a stratified nested 10-fold cross-validation to chose the best hyperparameters sets, that are $\lambda$ for models where we use EasyMKL and $C$ for all baselines and methods since we always use a SVM as base learner.
+In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
+The hyperparameters are $\lambda\in\{0,0.1,0.2,\dots,1\}-\{0.5\}$ for models where we use EasyMKL and $C\in\{2^i, i:-3\dots6\}$.
+Note that for all baselines we need to calculate all kernel matrices using all of training data.
 
-\subsection{Results}
-[...]
+The datasets used in our experiments are: [???]
+
+The results of our experiments are showed in \tablename\ \ref{tab:res}.
+
 \begin{table}[]
@@
 \caption{My caption}
-\label{my-label}
+\label{tab:res}
 \resizebox{\textwidth}{!}{

### 2016-11-24 paper.tex
Modified introduction and background

--- 2016-11-24 paper.tex
@@
 Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
-In these cases, specific machine learning techniques have to be adopted.
-Kernel methods are one option, where it suffices to adopt a kernel function defined for the kind of data under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.
+In these cases, derive a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
+Another option is to deal directly with examples represented in a structured form.
+In this case, specific machine learning techniques have to be adopted.
+Kernel methods are one option, where it suffices to adopt a kernel function defined for data type under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.
 
@@
 The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
-Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii)the hyper-parameters of the learning algorithm.
-A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these paraeters are referres to as \textit{parameters grid}).
+Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii) the hyper-parameters of the learning algorithm.
+A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
 Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
 
-The learning algorithm has to be trained for each hyper-parameter combination, and this procedure may be very time consuming.
+With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
 A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
-In the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of their hyper-parameters combination.
+However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid.
 This step can also be time consuming, especially when dealing with data in a structured form.
-In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of manitude on real-world datasets.
+
+In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.
 
 %\section{Kernel for structures and Multiple Kernel Learning}
-\section{Backgroung}
+\section{Background}
+A kernel method is composed by the following two modules.
+A learning algorithm, that expresses the solution only via dot products between training examples.
+A kernel function ${k}: \mathcal{X} \times \mathcal{X} \rightarrow \mathbb{R}$ that is a symmetric positive semi-definite function that corresponds to a dot product in a Reproducing Kernel Hilbert Space (RKHS), i.e.
+there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(X_i,X_j) = \langle \phi(X_i),\phi(X_j) \rangle$ with $X_i,X_j \in \mathcal{X}$.%~\cite{559923}.
 When dealing with structured data, the choice of the kernel to adopt is a key step.
 Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).
+
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\cite{Shervashidze2009} .
+A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
+A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
+In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity).
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
 In the following we will give some details about the considered alternatives.
-\textcolor{red}{TODO}\\
-\begin{itemize}
- \item WL
- \item NSPDK
- \item ODD$_{ST}$
-\end{itemize}
+Each kernel restricts to specific kinds of subgraphs, up to a certain dimension (that, in general, is a kernel parameter).
+Note that it is out of the scope of this paper to give an extensive comparison among the various graph kernels.
+
+The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ in the two input graphs.
+The complexity of the kernel is $O(|E|h)$.
+While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
+Note that the subtree-walks extracted by the kernel differ from  subtree structures because a node can appear multiple times in the same subtree-walk.
+
+In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK), an extension of the WL Fast Subtree Kernel, is presented.
+This kernel computes the exact matches between pairs of subgraphs with controlled size and distance.
+Their kernel, has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
+% The complexity of the kernel is $O(|V| |V_h| |E_h| \log |E_h|)$, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
+The authors state that, for small values of the subgraph size and distance, the complexity of the kernel becomes in practice linear.
+
+The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs (Figure~\ref{fig3:graph}).
+It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
+Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
+The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
 

### 2016-11-24 paper.tex

@@
 \bibliographystyle{unsrt}
-\bibliography{donini,biblio,Mendeley}
+\bibliography{donini,biblio}
 

### 2016-11-24 paper.tex
Fixed bug in merge.. git sucks for tex

@@
 
-The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs (Figure~\ref{fig3:graph}).
+The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
 It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.

### 2016-11-24 paper.tex
typos

@@
 A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
-A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
+%A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
 In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity).
@@
 The complexity of the kernel is $O(|E|h)$.
-While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
+%While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
 Note that the subtree-walks extracted by the kernel differ from  subtree structures because a node can appear multiple times in the same subtree-walk.
@@
 Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
-The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
+The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
 
@@
 
-\section{Our framework}
-Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be expensive.
+\section{Proposed framework}
+Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high.
 Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
-In order to avoid this problem, we propose a method to reduce the number of kernels, based on the robustness of combination vector $\eta$.\\
-In particular if $\eta$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
+In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
+In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
 In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.

### 2016-11-24 paper.tex
Modified experimental results

@@
 there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(X_i,X_j) = \langle \phi(X_i),\phi(X_j) \rangle$ with $X_i,X_j \in \mathcal{X}$.%~\cite{559923}.
+\textcolor{red}{TODO definire kernel matrix}
 When dealing with structured data, the choice of the kernel to adopt is a key step.
@@
 In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
-In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\eta_s$ learned using the same kernels calculated on a subset of data, then we can use directly $\eta_s$ in our model.
-In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
-Furthermore, we can use values in $\eta_s$ to perform a ranking over kernels, removing those below a threshold.
-Then we fit the model using only the top kernels selected.
+In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
+%In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
+Moreover, we can use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
+Then we compute the kernel matrix, on all the available data, for just the top kernels, and fit a model combining them.
 
-In summary, in the first phase we chose the top kernels using a subset of data, in the latter, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
+%In summary, in the first phase we choose the top kernels using a subset of the available data.
+In the second phase, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
 
-\section{Experimental Results (settings?)}
+\section{Experimental Assessment}
 Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
@@
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=\textwidth]{img/weights_GDD.png}
-\caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
-\label{fig:weights}
-\end{figure}
+% \begin{figure}[!htb]
+% \centering
+% \includegraphics[width=\textwidth]{img/weights_GDD.png}
+% \caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
+% \label{fig:weights}
+% \end{figure}
 

### 2016-11-24 paper.tex
Added dataset description

@@
 \usepackage{amssymb,amsmath,array}
+\usepackage[utf8]{inputenc}
 %\usepackage{color}
@@
 %style file for ESANN manuscripts
-\title{Title}
+%primo tentativo
+\title{Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning}
 
@@
 %\author{First author$^1$ and Second author$^2$
-\author{A$^1$, B$^2$ and C$^3$
+\author{Michele Domini$^1$, Nicol\`o Navarin$^2$, Ivano Lauriola$^2$, Fabio Aiolli$^2$ and Fabrizio Costa$^3$
 %
@@
 % Addresses and institutions (remove "1- " in case of a single institution)
-1- Department of Mathematics, University of Padova\\
+1- Computational Statistics and Machine Learning (CSML) \\
+Istituto Italiano di Tecnologia, Via Morego 30, Genova, Italy
+\vspace{.1cm}\\
+2- Department of Mathematics, University of Padova\\
 via Trieste 63, Padova, Italy
-\vspace{.1cm}\\
-2- Computational Statistics and Machine Learning (CSML) \\
-Istituto Italiano di Tecnologia, Via Morego 30, Genova, Italy
 \vspace{.1cm}\\
@@
 A kernel function ${k}: \mathcal{X} \times \mathcal{X} \rightarrow \mathbb{R}$ that is a symmetric positive semi-definite function that corresponds to a dot product in a Reproducing Kernel Hilbert Space (RKHS), i.e.
-there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(X_i,X_j) = \langle \phi(X_i),\phi(X_j) \rangle$ with $X_i,X_j \in \mathcal{X}$.%~\cite{559923}.
-\textcolor{red}{TODO definire kernel matrix}
+there exists a $\phi: \mathcal{X} \rightarrow \mathcal{K} \subseteq \mathbb{R}^D$, where $\mathcal{X}$ is the input space and $\mathcal{K}$ is an Hilbert space (commonly referred to as \textit{feature space}), such that $k(x_i,x_j) = \langle \phi(x_i),\phi(x_j) \rangle$ with $x_i,x_j \in \mathcal{X}$.
+%~\cite{559923}.
+%\textcolor{red}{TODO definire kernel matrix}
+A kernel (or \textit{Gram}) matrix for a set of examples $Tr=\{x_1, \ldots, x_l\}$ is an $l \times l$ matrix $G$ with entries $\{G\}_{ij}=k(x_i,x_j)$.
 When dealing with structured data, the choice of the kernel to adopt is a key step.
@@
 
-The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ in the two input graphs.
+The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
 The complexity of the kernel is $O(|E|h)$.
@@
 In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK), an extension of the WL Fast Subtree Kernel, is presented.
-This kernel computes the exact matches between pairs of subgraphs with controlled size and distance.
-Their kernel, has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
+This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).
+The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
 % The complexity of the kernel is $O(|V| |V_h| |E_h| \log |E_h|)$, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
@@
 
-The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
-It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
-Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
-The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
+The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{Dasan2012,DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
+It exploits the shortest-path (up to length $h$, a hyper-parameter) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
+Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting hyper-parameter.
+The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
 
@@
 \section{Experimental Assessment}
+We conducted our experiments on five real-world datasets:
+AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
+CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
+The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
+All the nodes are labelled and there are no self loops.
+The AIDS dataset contains 1503 chemical compounds, labelled according to
+their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
+compounds respectively; NCI1 consists of 4110 chemical compounds screened for activity against 
+non-small lung cancer cells; GDD is composed of 1178 X-ray crystal structures of
+proteins.
+
 Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.

### 2016-11-24 paper.tex
Modified dataset description

@@
 \section{Experimental Assessment}
-We conducted our experiments on five real-world datasets:
-AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
-CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
-The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
+We conducted our experiments on five real-world datasets (see \cite{DaSanMartino2016} for a more detailed description).
+%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
+%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
+%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
 All the nodes are labelled and there are no self loops.
-The AIDS dataset contains 1503 chemical compounds, labelled according to
+The AIDS dataset contains 1503 chemical compounds (encoded in graph form), labelled according to
 their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
@@
 proteins.
+All the datsets represent binary classification problems.
 

### 2016-11-25 paper.tex
experiments

@@
 \newcommand{\pphi}{\pmb{\phi}}
+
 \newcommand{\res}[2]{$#1_{\pm#2}$}
+
+\newcommand{\kval}{$K_{\textsc{val}}$}
+\newcommand{\ksum}{$K_{\textsc{sum}}$}
+\newcommand{\kmkl}{$K_{\textsc{mkl}}$}
+\newcommand{\ksmkl}{$K_{\textsc{mkl}}^{sub}$}
+\newcommand{\kssum}{$K_{\textsc{sum}}^{sub}$}
+\newcommand{\ksw}{$K_{\textsc{w}}^{sub}$}
 
@@
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
 In the following we will give some details about the considered alternatives.
@@
 
-The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{NIPS2009_0533}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
+The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{Shervashidze2011}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
 The complexity of the kernel is $O(|E|h)$.
@@
 the difference between the true error and the empirical margin error).
-These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Srebro2006,Cortes2009c,Hussain2011,Hussain2011a}.
+These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Srebro2006,Cortes2009c}%,Hussain2011,Hussain2011a}.
 %,Kakade2009,Micchelli2005,Kloft2012
@@
 They usually get results scalable with respect to the number of kernels combined but their effectiveness critically depends on the domain at hand.
-They use a parameterized combination function and find the parameters of this function generally by looking at some measure obtained from each kernel separately,  often giving a suboptimal solution (since no information sharing among the kernels is exploited).
+%They use a parameterized combination function and find the parameters of this function generally by looking at some measure obtained from each kernel separately,  often giving a suboptimal solution (since no information sharing among the kernels is exploited).
 
-On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine (e.g.
-structural risk based target function) or formulated as a different model (e.g.
-alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Bach2004,Varma2009}.
-%,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010
+On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine %(e.g.
+structural risk based target function)
+or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Bach2004,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010
 
@@
 This equation is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}.
-The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation.
+%The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation.
 Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$).
 From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
-\begin{equation}
-\label{eq:easyeta}
-	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
-\end{equation}
+%\begin{equation}
+%\label{eq:easyeta}
+%	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
+%\end{equation}
 
@@
 
-Firstly, we performed some experiments to observe how many samples are required to make $\eta$ and $\eta_s$ similar.
-The metric used for comparison is the jaccard similarity score. Indeed, in our context two weights vectors are similar is they provide the same top kernels.
-These experiments are summarized in \figurename\ \ref{fig:weights} and \ref{fig:jaccard}.
-
-% \begin{figure}[!htb]
-% \centering
-% \includegraphics[width=\textwidth]{img/weights_GDD.png}
-% \caption{The weights vector learned by EasyMKL using $50\%$ and $25\%$ of training data. Blue regions represents the comparison with the weights vector calculated using all data.}
-% \label{fig:weights}
-% \end{figure}
+Firstly, we performed some experiments to check how many samples are required to make $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ similar.
+In our context two weights vectors are similar if they provide the same top kernels.
+By the way the metric used for comparison is the jaccard similarity score.
+\figurename\ \ref{fig:jaccard} show the jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
+From other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
 
@@
 \centering
-\subfloat[a]{\includegraphics[width=0.42\textwidth]{img/CPDB_jaccard.png}}
-\subfloat[b]{\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}}
+\includegraphics[width=0.42\textwidth]{img/CPDB_jaccard.png}
+\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}
 \caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
@@
 
-In the first step of our method, we learn the weights vector $\eta_{10}$ using a subset $(10\%)$ of training data and the whole set of kernels.
-To do this, we perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner.
-The hyperparameters are $(\lambda,C)$.
-Then we fit the model with the best combination and chose the top $10\%$ kernels.\\
-In the latter step we calculate the top kernel matrices and combine it to get the kernel. We propose three methods to perform this combination:
-\begin{itemize}
-\item{}use the EasyMKL algorithm;
-\item{}calculate the average of kernels;
-\item{}use the same weights (rescaled) from the first learning step.
-\end{itemize}
-For testing, we compared our method with 3 hard baselines, that are:
-\begin{itemize}
-\item{}validation: we select the kernel which has the best result in validation;
-\item{}average: we calculate the kernel as the average of all base kernels;
-\item{}combined: we use EasyMKL to combine the whole set of kernels;
-\end{itemize}
+To learn $\hat{\boldsymbol{\eta}}$ we chose a random subsampling of training data and perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner.
+Then we fit the model with the best combination and select the top kernels.
+In the second step we calculate the top kernel matrices using the whole training data and combine it to get the kernel. We propose 3 different methods to perform this combination:
+(1)\ksmkl: use the EasyMKL algorithm, (2)\kssum: calculate the average of kernels, (3)\ksw: use the same weights (rescaled) from the first learning step.\\
+For testing, we compared our method against 3 hard baselines, that are: (a)\kval: the kernel is selected in the nested-cv procedure, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: we use EasyMKL to combine the whole set of kernels.\\
 In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
-The hyperparameters are $\lambda\in\{0,0.1,0.2,\dots,1\}-\{0.5\}$ for models where we use EasyMKL and $C\in\{2^i, i:-3\dots6\}$.
-Note that for all baselines we need to calculate all kernel matrices using all of training data.
-
-The datasets used in our experiments are: [???]
+The hyperparameters are $\lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL and $C\in\{2^i, i:-3\dots6\}$.
+Note that for all baselines we need to calculate all kernel matrices using all of training data.\\
+The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
 
@@
 \resizebox{\textwidth}{!}{
-\begin{tabular}{l|c|lll|lll}
+\begin{tabular}{l|c|ccc|ccc}
 \hline
-dataset & \# train & validation      & all (easy) & all (average) & subset\_easy & subset\_aver & subset\_w \\
+dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
 \hline
+MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{0.9331}{0.053}    \\
+&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
 CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $0.8850_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
-\\
-MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{0.9331}{0.053}    \\
-\\
+&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
+GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+&			& +24h	& +24h	& +24h	&3h		& 4h 15m		& 4h 15m\\\hline
+AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
+NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{0.8851}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
+NCI109 & 4127 & \res{0.8728}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
 CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.11} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
-\\
-GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.869}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
-\\
-AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
-\\
-NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{0.8851}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
-\\
-NCI109 & 4127 & \res{0.8728}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
-\\
+&	&	38h	&-	& 4h 26m		&176h	& 1h 34m		& 1h 34m\\
 \hline

### 2016-11-25 paper.tex
experiments

@@
 \figurename\ \ref{fig:jaccard} show the jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
-From other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
+According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
 
@@
 In the second step we calculate the top kernel matrices using the whole training data and combine it to get the kernel. We propose 3 different methods to perform this combination:
-(1)\ksmkl: use the EasyMKL algorithm, (2)\kssum: calculate the average of kernels, (3)\ksw: use the same weights (rescaled) from the first learning step.\\
-For testing, we compared our method against 3 hard baselines, that are: (a)\kval: the kernel is selected in the nested-cv procedure, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: we use EasyMKL to combine the whole set of kernels.\\
+(1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.\\
+For testing, we compared our method against 3 hard baselines, that are: (a)\kval: the kernel is selected in the nested-cv procedure, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: we use EasyMKL to combine the whole set of kernels.
 In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
-The hyperparameters are $\lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL and $C\in\{2^i, i:-3\dots6\}$.
-Note that for all baselines we need to calculate all kernel matrices using all of training data.\\
+The hyperparameters are $\lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL, and $C\in\{2^i, i:-3\dots6\}$.
+Note that for all baselines we need to calculate all kernel matrices using all of training data directly.\\
 The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.

### 2016-11-25 paper.tex
experiments

@@
 \centering
-\caption{My caption}
-\label{tab:res}
 \resizebox{\textwidth}{!}{
@@
 &	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
-CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.11} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
 &	&	38h	&-	& 4h 26m		&176h	& 1h 34m		& 1h 34m\\
@@
 \end{tabular}}
+\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
+\label{tab:res}
 \end{table}

### 2016-11-25 paper.tex
Removing some references of MKL

@@
  %structured sparsity regularizers \cite{Micchelli2010,Micchelli2013}.
-The problem of searching for a combinations of basic kernels can be rephrased as a regularization problem in which the prediction function is the sum of functions $f_r$ in the RKHS of kernel $\KK_r$ and the regularization term is the combination of the norms of the $f_r$ in the associated RKHS \cite{Micchelli2005a}.
+%The problem of searching for a combinations of basic kernels can be rephrased as a regularization problem in which the prediction function is the sum of functions $f_r$ in the RKHS of kernel $\KK_r$ and the regularization term is the combination of the norms of the $f_r$ in the associated RKHS \cite{Micchelli2005a}.
 %,Micchelli2007
-For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.
+%For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.
 

### 2016-11-25 paper.tex

@@
 With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
-A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
+A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
 However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid.
@@
 
-In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.
+In this paper, we propose a new approach to parameter selection that, based on sub-sampling and MKL, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.
 
@@
 
-\subsection{Multiple Kernel Learning (MKL)}
+\subsection{Multiple Kernel Learning}
 \label{MKL}

### 2016-11-25 paper.tex
Modified dataset description

@@
 %The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
-All the nodes are labelled and there are no self loops.
-The AIDS dataset contains 1503 chemical compounds (encoded in graph form), labelled according to
-their antiviral activity; CAS and CPDB store 4337 and 684 mutagenic
-compounds respectively; NCI1 consists of 4110 chemical compounds screened for activity against 
-non-small lung cancer cells; GDD is composed of 1178 X-ray crystal structures of
+All the nodes are labeled and there are no self loops.
+The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
+their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 consists of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of
 proteins.
-All the datsets represent binary classification problems.
+All the datasets represent binary classification problems.
 
@@
 By the way the metric used for comparison is the jaccard similarity score.
-\figurename\ \ref{fig:jaccard} show the jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
+\figurename\ \ref{fig:jaccard} show the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
 According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.

### 2016-11-25 paper.tex
Modified Lambda of EasyMKL

@@
 \label{eq:easymklotig}
-\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \lambda ||\boldsymbol{\gamma}||^2.
+\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2.
 \end{equation}
@@
 
-where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\lambda$ is a regularization hyper-parameter.
+where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyper-parameter.
 The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
@@
 The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
-their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 consists of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of
+their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of
 proteins.
@@
 In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
-The hyperparameters are $\lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL, and $C\in\{2^i, i:-3\dots6\}$.
+The hyperparameters are $\Lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL, and $C\in\{2^i, i:-3\dots6\}$.
 Note that for all baselines we need to calculate all kernel matrices using all of training data directly.\\

### 2016-11-25 paper.tex
little things about EasyMKL

@@
 At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
-
-The objective function in Eq.
-\ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
-This equation is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}.
+%The objective function in Eq. \ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
+Eq.
+\ref{eq:easymklotig} is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}.
 %The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation.
@@
 
-In the following sections, we will refer to this algorithm as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
+In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
 %and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyper-parameter $\Lambda$.

### 2016-11-25 paper.tex
Typos

--- 2016-11-25 paper.tex
@@
 When dealing with structured data, the choice of the kernel to adopt is a key step.
-Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).
+Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between expressiveness and efficiency.
+%(of course, this trade-off depends from the considered task).
 
@@
 Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
-In the following we will give some details about the considered alternatives.
-Each kernel restricts to specific kinds of subgraphs, up to a certain dimension (that, in general, is a kernel parameter).
+%In the following we will give some details about the considered alternatives.
+Each one of these kernels considers only specific kinds of subgraphs, up to a certain dimension (that, in general, is a kernel parameter).
 Note that it is out of the scope of this paper to give an extensive comparison among the various graph kernels.
@@
 
-In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK), an extension of the WL Fast Subtree Kernel, is presented.
+In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK) is presented.
 This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).

### 2016-11-26 paper.tex
abstract

@@
 %primo tentativo
-\title{Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning}
+\title{Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning}
 
@@
 \begin{abstract}
-...
+Kernel for structures are generally characterized by a number of hyper-parameter which need to be tuned.
+Moreover, different types of kernels can be used and the best choice usually depends on data.
+The hyper-parameter setting is a time-consuming step.
+One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyper-parameters settings.
+However, this solution still requires the computation of many large kernel matrices.
+In this paper we propose a subsampling method to efficiently select a small number of kernels which need to be actually computed.
+Finally, we give empirical evidence that the method proposed is far more efficient than the other approaches while maintaining similar results in terms of AUC.
 \end{abstract}
@@
 \section{Experimental Assessment}
-We conducted our experiments on five real-world datasets (see \cite{DaSanMartino2016} for a more detailed description).
+We conducted our experiments on several real-world binary datasets (see \cite{DaSanMartino2016} for a more detailed description).
 %AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
@@
 %The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
+The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
+their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
+[...].
 All the nodes are labeled and there are no self loops.
-The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
-their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of
-proteins.
-All the datasets represent binary classification problems.
+
+The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
+%These are always calculated for all of our baselines, 
+The baselines consist on a SVM with kernels (a)\kval: the kernel is the one which has the best validation score, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: the kernel is a combination of all base kernels using EasyMKL.
 
@@
 By the way the metric used for comparison is the jaccard similarity score.
-\figurename\ \ref{fig:jaccard} show the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
+\figurename\ \ref{fig:jaccard} shows the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
 According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
@@
 (1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.\\
-For testing, we compared our method against 3 hard baselines, that are: (a)\kval: the kernel is selected in the nested-cv procedure, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: we use EasyMKL to combine the whole set of kernels.
 In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
@@
 Note that for all baselines we need to calculate all kernel matrices using all of training data directly.\\
-The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
 
@@
 \begin{tabular}{l|c|ccc|ccc}
-\hline
+\hline\hline
 dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
@@
 &	&	38h	&-	& 4h 26m		&176h	& 1h 34m		& 1h 34m\\
-\hline
+\hline\hline
 \end{tabular}}

### 2016-11-26 paper.tex
experimental assessment

@@
 \section{Experimental Assessment}
-We conducted our experiments on several real-world binary datasets (see \cite{DaSanMartino2016} for a more detailed description).
+We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016} for a more detailed description).
 %AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
@@
 %The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
-The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
+{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
 their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
 [...].
-All the nodes are labeled and there are no self loops.
+All the nodes are labeled and there are no self loops.}
 
 The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
-%These are always calculated for all of our baselines, 
-The baselines consist on a SVM with kernels (a)\kval: the kernel is the one which has the best validation score, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: the kernel is a combination of all base kernels using EasyMKL.
+In all models, we considered kernels calculated in less that 1 hour, rejecting others.
+The baselines used to compare our method consist on a SVM with kernels (a)\kval: the kernel is the one which has the best validation score, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: the kernel is a combination of all base kernels using EasyMKL.
+For each baseline, the computation of all kernels is required.
+The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for \kmkl.
 
@@
 According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
+Except for MUTAG, where we use 20\% of training data.
 
@@
 In the second step we calculate the top kernel matrices using the whole training data and combine it to get the kernel. We propose 3 different methods to perform this combination:
-(1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.\\
-In all models, we use a SVM as base learner, and we select the hyperparameters using a nested 10-fold CV procedure.
-The hyperparameters are $\Lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for models where we use EasyMKL, and $C\in\{2^i, i:-3\dots6\}$.
-Note that for all baselines we need to calculate all kernel matrices using all of training data directly.\\
-
-The results of our experiments are showed in \tablename\ \ref{tab:res}.
+(1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.
+In all of these methods we use a SVM as base learner. The hyperparameters sets are the same used in baselines.\\
+\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.
 
@@
 GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
-&			& +24h	& +24h	& +24h	&3h		& 4h 15m		& 4h 15m\\\hline
+&			& $>$24h	& $>$24h	& $>$24h	&3h		& 4h 15m		& 4h 15m\\\hline
 AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
@@
 \section{Conclusion}
-...
+In the context of MKL, we showed a procedure to learn the kernels combination vector using a subset of training data, and use this vector to chose the top kernels for a given problem.
+Then we propose 3 methods to combine top kernels quickly, preserving an high AUC score.
+[...]
 

### 2016-11-26 paper.tex
>48h

@@
 GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
-&			& $>$24h	& $>$24h	& $>$24h	&3h		& 4h 15m		& 4h 15m\\\hline
+&			& $>$48h	& $>$48h	& $>$48h	&3h		& 4h 15m		& 4h 15m\\\hline
 AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\

### 2016-11-26 paper.tex
modifiche di Fabio

@@
 Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
-In these cases, derive a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
+In these cases, deriving a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
 Another option is to deal directly with examples represented in a structured form.
@@
 
-With kernel methods, a user has usually to deal with a number of hyper-parameters to fix at hand.
+With kernel methods, a user has usually to deal with several of hyper-parameters to fix manually.
 The optimization of these hyper-parameters can strongly affect the predictive performance of the method.

### 2016-11-26 paper.tex
removed half page

@@
 \newcommand{\ksw}{$K_{\textsc{w}}^{sub}$}
+
+\renewcommand{\baselinestretch}{.96}
 
@@
 \label{MKL}
-MKL \cite{Bach2004,Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
+MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
 The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
@@
 the difference between the true error and the empirical margin error).
-These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Srebro2006,Cortes2009c}%,Hussain2011,Hussain2011a}.
-%,Kakade2009,Micchelli2005,Kloft2012
+These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Cortes2009c}%,Hussain2011,Hussain2011a}.
+%,Kakade2009,Micchelli2005,Kloft2012,Srebro2006,
 
@@
 structural risk based target function)
-or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Bach2004,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010
+or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010,Bach2004
 
@@
 Specifically, its computational complexity is constant in memory and linear in time.
-
 EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples.
@@
 \label{eq:easymklotig}
-\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2.
+\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2,
 \end{equation}
-\vspace{-0.3cm}
-
+%\vspace{-0.1cm}
 where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyper-parameter.
@@
 %\end{equation}
-
 In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
@@
 
-The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8,0.9,1.0,1.1,1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
+The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
 In all models, we considered kernels calculated in less that 1 hour, rejecting others.
@@
 For each baseline, the computation of all kernels is required.
-The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots0.4,0.6\dots1\}$ for \kmkl.
+The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.
 

### 2016-11-26 paper.tex
quanto cavolo sono pro

@@
 \newcommand{\ksw}{$K_{\textsc{w}}^{sub}$}
+\newcommand{\tb}[1]{\boldsymbol{#1}}
 
@@
 \hline
-MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{0.9331}{0.053}    \\
+MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
 &			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
-CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $0.8850_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
+CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
 &			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
-GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
-&			& $>$48h	& $>$48h	& $>$48h	&3h		& 4h 15m		& 4h 15m\\\hline
-AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
+AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
 &		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
-NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{0.8851}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
 &	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
-NCI109 & 4127 & \res{0.8728}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
 &	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
-CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
-&	&	38h	&-	& 4h 26m		&176h	& 1h 34m		& 1h 34m\\
+CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
 \hline\hline
@@
 Then we propose 3 methods to combine top kernels quickly, preserving an high AUC score.
-[...]
+As showed in the results table, the percentage of subsampling and top kernels selected (10\%) is a good compromise between time complexity and high AUC score.
+Furthermore, due to low percentage, we can assume that all top kernels are good kernels for our problem, so we can combine them effectively using the simple summation, avoiding to use the EasyMKL algorithms in the second learning step.\\
+Finally, our method is able to reduce effectively the time complexity, making the MKL approach usable for huge datasets.
 

### 2016-11-26 paper.tex
small fixes

@@
 %\author{First author$^1$ and Second author$^2$
-\author{Michele Domini$^1$, Nicol\`o Navarin$^2$, Ivano Lauriola$^2$, Fabio Aiolli$^2$ and Fabrizio Costa$^3$
+\author{Michele Donini$^1$, Nicol\`o Navarin$^2$, Ivano Lauriola$^2$, Fabio Aiolli$^2$ and Fabrizio Costa$^3$
 %
@@
 
-\section{Conclusion}
+\section{Discussion and conclusion}
 In the context of MKL, we showed a procedure to learn the kernels combination vector using a subset of training data, and use this vector to chose the top kernels for a given problem.

### 2016-11-26 paper.tex
Cut some parts. Now it's 6 pages

--- 2016-11-26 paper.tex
@@
 A kernel (or \textit{Gram}) matrix for a set of examples $Tr=\{x_1, \ldots, x_l\}$ is an $l \times l$ matrix $G$ with entries $\{G\}_{ij}=k(x_i,x_j)$.
+
 When dealing with structured data, the choice of the kernel to adopt is a key step.
-Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between expressiveness and efficiency.
+% Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between expressiveness and efficiency.
 %(of course, this trade-off depends from the considered task).
-
+%
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
+%A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
 %A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
-In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity).
+In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004},
+%($O(n^3)$ computational complexity)
+shortest paths~\cite{Kriegel05shortestpath},
+ %($O(n^4)$ computational complexity),
+ subgraphs up to a fixed size $h$~\cite{Shervashidze2009}.
+ % ($O(n^h)$ complexity). 
  The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,DaSanMartino2016}, and these are the ones we focus on in this paper.
 %In the following we will give some details about the considered alternatives.
@@
 The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{Shervashidze2011}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
-The complexity of the kernel is $O(|E|h)$.
+%The complexity of the kernel is $O(|E|h)$.
 %While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
@@
 This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).
-The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
+%The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
 % The complexity of the kernel is $O(|V| |V_h| |E_h| \log |E_h|)$, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
-The authors state that, for small values of the subgraph size and distance, the complexity of the kernel becomes in practice linear.
+%The authors state that, for small values of the subgraph size and distance, the complexity of the kernel becomes in practice linear.
 
-The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{Dasan2012,DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
+The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
 It exploits the shortest-path (up to length $h$, a hyper-parameter) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
 Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting hyper-parameter.
-The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
+%The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
 
@@
 
-Existing MKL approaches can be divided in two main categories.
+%Existing MKL approaches can be divided in two main categories.
 In the first category, \emph{Fixed or Heuristic}, some fixed rule is applied to obtain the combination.
@@
 %They use a parameterized combination function and find the parameters of this function generally by looking at some measure obtained from each kernel separately,  often giving a suboptimal solution (since no information sharing among the kernels is exploited).
-
-On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine %(e.g.
+%
+%On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine %(e.g.
 structural risk based target function)
-or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010,Bach2004
+%or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010,Bach2004
 
@@
 \section{Experimental Assessment}
-We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016} for a more detailed description).
+We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016,Shervashidze2011} for a more detailed description).
 %AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
@@
 %The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
-{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
-their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
-[...].
-All the nodes are labeled and there are no self loops.}
-
+%{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
+%[...].
+%All the nodes are labeled and there are no self loops.}
+%
 The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.

### 2016-11-26 paper.tex
Switched one reference

@@
 \begin{abstract}
-Kernel for structures are generally characterized by a number of hyper-parameter which need to be tuned.
+Kernels for structures are generally characterised by a number of hyper-parameters which need to be tuned.
 Moreover, different types of kernels can be used and the best choice usually depends on data.
@@
 However, this solution still requires the computation of many large kernel matrices.
-In this paper we propose a subsampling method to efficiently select a small number of kernels which need to be actually computed.
+In this paper we propose a subsampling method to efficiently select just a small number of kernels which need to be actually computed.
 Finally, we give empirical evidence that the method proposed is far more efficient than the other approaches while maintaining similar results in terms of AUC.
@@
 With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
-A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
+A possible alleviation to this problem has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
 However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid.
@@
 \label{MKL}
-MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
+MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
 The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
@@
 %
-The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
+The kernels used in our experiments are:  NSPDK  with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$,  ODD$_{ST}$ with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, WL with $h \in \{0,1\dots9\}$.
 In all models, we considered kernels calculated in less that 1 hour, rejecting others.

### 2016-11-26 paper.tex
Last modifications

@@
 %primo tentativo
-\title{Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning}
+\title{Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning}
 
@@
 \begin{abstract}
-Kernels for structures are generally characterised by a number of hyper-parameters which need to be tuned.
+Kernels for structures are generally characterised by a number of hyperparameters which need to be tuned.
 Moreover, different types of kernels can be used and the best choice usually depends on data.
-The hyper-parameter setting is a time-consuming step.
-One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyper-parameters settings.
+The hyperparameter setting is a time-consuming step.
+One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyperparameters settings.
 However, this solution still requires the computation of many large kernel matrices.
@@
 
-With kernel methods, a user has usually to deal with several of hyper-parameters to fix manually.
-The optimization of these hyper-parameters can strongly affect the predictive performance of the method.
-Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyper-parameters of the selected kernel; (iii) the hyper-parameters of the learning algorithm.
-A commonly adopted and simple approach to hyper-parameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
+With kernel methods, a user has usually to deal with several of hyperparameters to fix manually. The optimization of these hyperparameters can strongly affect the predictive performance of the method.
+Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyperparameters of the selected kernel; (iii) the hyperparameters of the learning algorithm.
+A commonly adopted and simple approach to hyperparameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
 Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
 
-With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
+With this approach, a learning procedure has to be performed for each hyperparameter combination, possibly making it very time consuming.
 A possible alleviation to this problem has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
-However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid.
+However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyperparameters values in the grid.
 This step can also be time consuming, especially when dealing with data in a structured form.
@@
 %($O(n^3)$ computational complexity)
-shortest paths~\cite{Kriegel05shortestpath},
+shortest paths~\cite{Kriegel05shortestpath}, or
  %($O(n^4)$ computational complexity),
@@
 
-The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{Shervashidze2011}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
+The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{Shervashidze2011}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyperparameter) in the two input graphs.
 %The complexity of the kernel is $O(|E|h)$.
@@
 In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK) is presented.
-This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).
+This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyperparameters $r$ and $d$, respectively).
 %The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
@@
 The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
-It exploits the shortest-path (up to length $h$, a hyper-parameter) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
-Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting hyper-parameter.
+It exploits the shortest-path (up to length $h$, a hyperparameter) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
+Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting hyperparameter.
 %The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
@@
 %\vspace{-0.1cm}
-where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyper-parameter.
+where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyperparameter.
 The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
@@
 In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
-%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyper-parameter $\Lambda$.
+%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.
 
@@
 In our context two weights vectors are similar if they provide the same top kernels.
-By the way the metric used for comparison is the jaccard similarity score.
+The metric used for comparison is the Jaccard similarity score.
 \figurename\ \ref{fig:jaccard} shows the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
-According to other preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%.
-Except for MUTAG, where we use 20\% of training data.
+According to preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%, except for MUTAG (the smallest datasets), where we use 20\% of training data.
 
@@
 In the context of MKL, we showed a procedure to learn the kernels combination vector using a subset of training data, and use this vector to chose the top kernels for a given problem.
-Then we propose 3 methods to combine top kernels quickly, preserving an high AUC score.
+Then we propose three methods to combine top kernels quickly, preserving an high AUC score.
 As showed in the results table, the percentage of subsampling and top kernels selected (10\%) is a good compromise between time complexity and high AUC score.
-Furthermore, due to low percentage, we can assume that all top kernels are good kernels for our problem, so we can combine them effectively using the simple summation, avoiding to use the EasyMKL algorithms in the second learning step.\\
+Furthermore, due to the low number of selected top kernels, we can assume that all of them are good kernels for our problem, so we can combine them effectively using the simple summation, avoiding to use the EasyMKL algorithms in the second learning step.\\
 Finally, our method is able to reduce effectively the time complexity, making the MKL approach usable for huge datasets.

### 2016-11-26 paper.tex
F

--- 2016-11-26 paper.tex
@@
 \newcommand{\ksw}{$K_{\textsc{w}}^{sub}$}
-\newcommand{\tb}[1]{\boldsymbol{#1}}
 
@@
 %\author{First author$^1$ and Second author$^2$
-\author{Michele Donini$^1$, Nicol\`o Navarin$^2$, Ivano Lauriola$^2$, Fabio Aiolli$^2$ and Fabrizio Costa$^3$
+\author{Michele Domini$^1$, Nicol\`o Navarin$^2$, Ivano Lauriola$^2$, Fabio Aiolli$^2$ and Fabrizio Costa$^3$
 %
@@
 \vspace{.1cm}\\
-3- ... \\
-...
+3- Department of Computer Science, Freiburg University \\
+Georges-Kohler-Allee 106, 79110 Freiburg, Germany\\
 }
@@
 A kernel (or \textit{Gram}) matrix for a set of examples $Tr=\{x_1, \ldots, x_l\}$ is an $l \times l$ matrix $G$ with entries $\{G\}_{ij}=k(x_i,x_j)$.
+When dealing with structured data, the choice of the kernel to adopt is a key step.
+Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between expressiveness and efficiency.
+%(of course, this trade-off depends from the considered task).
 
-When dealing with structured data, the choice of the kernel to adopt is a key step.
-% Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between expressiveness and efficiency.
-%(of course, this trade-off depends from the considered task).
-%
 In this paper we focus on graphs, i.e. we consider each example to be a different graph.
-%A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
+A graph is a tuple $G=(V_G,E_G,L_G)$, where $V_G=\{v_1,\ldots,v_n\}$ is the set of vertices, $E_G=\{(u,v) | u,v \in V_G\}$ is the set of edges (with $|E_G|=m$), and $L_G: V_G \rightarrow \Sigma$ is a function mapping each vertex to a discrete label in a fixed alphabet $\Sigma$.
 %A graph is undirected if $(u,v)\in E_g \Rightarrow (v,u) \in E_G$, otherwise it is directed.
-In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004},
-%($O(n^3)$ computational complexity)
-shortest paths~\cite{Kriegel05shortestpath},
- %($O(n^4)$ computational complexity),
- subgraphs up to a fixed size $h$~\cite{Shervashidze2009}.
- % ($O(n^h)$ complexity). 
+In this setting, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size $h$~\cite{Shervashidze2009} ($O(n^h)$ complexity).
 The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
-Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,DaSanMartino2016}, and these are the ones we focus on in this paper.
+Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus on in this paper.
 %In the following we will give some details about the considered alternatives.
@@
 The Weisfeiler-Lehman Fast Subtree kernel (WL)~\cite{Shervashidze2011}  counts the number of identical subtree patterns obtained by subtree-walks up to height $h$ (an hyper-parameter) in the two input graphs.
-%The complexity of the kernel is $O(|E|h)$.
+The complexity of the kernel is $O(|E|h)$.
 %While being fast to compute, the kernel may lack of expressiveness for some tasks given that the number of non-zero features generated by one graph is at most $|V|h$. 
@@
 This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).
-%The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
+The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
 % The complexity of the kernel is $O(|V| |V_h| |E_h| \log |E_h|)$, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
-%The authors state that, for small values of the subgraph size and distance, the complexity of the kernel becomes in practice linear.
+The authors state that, for small values of the subgraph size and distance, the complexity of the kernel becomes in practice linear.
 
-The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
+The Ordered Decomposition DAGs Subtree kernel (ODD$_{ST}$)~\cite{Dasan2012,DaSanMartino2016} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
 It exploits the shortest-path (up to length $h$, a hyper-parameter) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
 Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting hyper-parameter.
-%The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
+The time complexity of the kernel is, under mild conditions, $O(|V_G| \log |V_G|)$.%, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
 
@@
 
-%Existing MKL approaches can be divided in two main categories.
+Existing MKL approaches can be divided in two main categories.
 In the first category, \emph{Fixed or Heuristic}, some fixed rule is applied to obtain the combination.
@@
 %They use a parameterized combination function and find the parameters of this function generally by looking at some measure obtained from each kernel separately,  often giving a suboptimal solution (since no information sharing among the kernels is exploited).
-%
-%On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine %(e.g.
+
+On the other hand, the \emph{Optimization based} approaches learn the combination parameters by solving a single optimization problem directly integrated in the learning machine %(e.g.
 structural risk based target function)
-%or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010,Bach2004
+or formulated as a different model (e.g. alignment, or other kernel similarity maximization) \cite{Rakotomamonjy2008,Varma2009}. %,Kloft2011,SorenSonnenburg2006,Vishwanathan2010,Xu2010,Bach2004
 
@@
 \section{Experimental Assessment}
-We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016,Shervashidze2011} for a more detailed description).
+We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016} for a more detailed description).
 %AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
@@
 %The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
-%{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
-%[...].
-%All the nodes are labeled and there are no self loops.}
-%
+{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to
+their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
+[...].
+All the nodes are labeled and there are no self loops.}
+
 The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
@@
 \hline
-MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
+MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{0.9331}{0.053}    \\
 &			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
-CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
+CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $0.8850_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
 &			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
-GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
-&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
-AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+GDD     & 1178 & \res{0.8647}{0.045} & \res{0.8719}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+&			& $>$48h	& $>$48h	& $>$48h	&3h		& 4h 15m		& 4h 15m\\\hline
+AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{0.7845}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
 &		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
-NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{0.8851}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
 &	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
-NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+NCI109 & 4127 & \res{0.8728}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
 &	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
-CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
-&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
+CAS     & 4337 & \res{0.9189}{0.012} & - & \res{0.9209}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+&	&	38h	&-	& 4h 26m		&176h	& 1h 34m		& 1h 34m\\
 \hline\hline
@@
 
-\section{Discussion and conclusion}
+\section{Conclusion}
 In the context of MKL, we showed a procedure to learn the kernels combination vector using a subset of training data, and use this vector to chose the top kernels for a given problem.
 Then we propose 3 methods to combine top kernels quickly, preserving an high AUC score.
-As showed in the results table, the percentage of subsampling and top kernels selected (10\%) is a good compromise between time complexity and high AUC score.
-Furthermore, due to low percentage, we can assume that all top kernels are good kernels for our problem, so we can combine them effectively using the simple summation, avoiding to use the EasyMKL algorithms in the second learning step.\\
-Finally, our method is able to reduce effectively the time complexity, making the MKL approach usable for huge datasets.
+[...]
 

### 2016-11-26 paper.tex
F

--- 2016-11-26 paper.tex
@@
 \begin{abstract}
-Kernels for structures are generally characterised by a number of hyperparameters which need to be tuned.
-Moreover, different types of kernels can be used and the best choice usually depends on data.
-The hyperparameter setting is a time-consuming step.
-One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyperparameters settings.
-However, this solution still requires the computation of many large kernel matrices.
-In this paper we propose a subsampling method to efficiently select just a small number of kernels which need to be actually computed.
-Finally, we give empirical evidence that the method proposed is far more efficient than the other approaches while maintaining similar results in terms of AUC.
+
+Model selection is one of the most computationally expensive tasks in a
+machine learning application. When dealing with kernel methods for structures,
+the choice with the largest impact on the overall performance is the selection
+of the feature bias, i.e. the choice of the concrete kernel for structures.
+Each kernel in turn exposes several hyper-parameters which also need to be
+fine tuned.  Multiple Kernel Learning offers a way to approach this
+computational bottleneck by generating a combination of different kernels
+under different parametric settings. However, this solution still requires the
+computation of many large kernel matrices. In this paper we propose a method
+to efficiently select just a small number of kernels without loss in
+predictive performance.
+
 \end{abstract}
@@
 \section{Introduction}
-In different real-world domains, it may be easy to encode examples in a structured form.
-For example, in chemoinformatics there is a well known graph representation of the secondary structures of chemical compounds.
-Moreover, images can easily be represented as graph after segmentation, where adjacent objects (or regions) are linked.
-In these cases, deriving a vectorial representation for the data may be a time-consuming task, where information from  domain experts is needed, and information loss is, in general, unavoidable.
-Another option is to deal directly with examples represented in a structured form.
-In this case, specific machine learning techniques have to be adopted.
-Kernel methods are one option, where it suffices to adopt a kernel function defined for data type under consideration. Then, standard (kernelized) learning algorithms (e.g. SVM) can be adopted.
+
+Many application domains can be naturally encoded in a structured form. In
+chemo- and bioinformatics for example, molecules and polymers can be encoded
+as graphs with atoms as nodes and chemical bonds as edges. After a
+segmentation pre-processing step, images can also be represented as networks
+of adjacent objects or regions. Working on these domains employing traditional
+feature engineering is possible, but it is generally time-consuming (every
+different application requires a novel feature design by some expert) and
+information loss is often unavoidable. Direct processing of structures is
+possible using a kernelized approach, where a kernel function can be devised
+for each generic data type (for example sequences, trees or graphs). This in
+turn allows to use standard learning algorithms (e.g. SVM) to solve the
+predictive task.
 

### 2016-11-26 paper.tex
F

@@
 
-With kernel methods, a user has usually to deal with several of hyperparameters to fix manually. The optimization of these hyperparameters can strongly affect the predictive performance of the method.
-Usually, these parameters are: (i) the choice of the kernel to adopt; (ii) the hyperparameters of the selected kernel; (iii) the hyperparameters of the learning algorithm.
-A commonly adopted and simple approach to hyperparameters optimization is to fix a-priori some possible values for each parameter (the combinations of these parameters are referred to as \textit{parameters grid}).
-Then, the learning algorithm is trained for each possible parameters combination, and its performances are evaluated. This approach is commonly referred to as grid-search.
-
-With this approach, a learning procedure has to be performed for each hyperparameter combination, possibly making it very time consuming.
-A possible alleviation to this problem has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
-However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyperparameters values in the grid.
-This step can also be time consuming, especially when dealing with data in a structured form.
-
-In this paper, we propose a new approach to parameter selection that, based on sub-sampling and MKL, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.
+Model selection is one of the most computationally expensive tasks in a
+machine learning application. When dealing with kernel methods for structures,
+the choice with the largest impact on the overall performance is the selection
+of the feature bias, i.e. the choice of the concrete kernel for structures.
+Each kernel in turn exposes several hyper-parameters which also need to be
+fine tuned. Finally, the downstream learning algorithm has its own hyper-
+parameters. A common approach to hyper-parameters optimization is to fix
+a-priori  a \textit{parameters grid}, i.e. a set of possible values for each
+parameter. Then, the predictive performance of the learning algorithm is
+evaluated for each possible parameters combination ({\em grid-search}
+strategy), which is possibly a very time consuming step.  A more efficient
+approach has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016},
+where instead of selecting the best parameters configuration, Multiple Kernel
+Learning (MKL) was used for combining different kernel matrices in a single
+learning procedure. While more efficient, this approach does not scale to very
+large datset since a kernel matrix has to be computed for each kernel and for
+each of its hyper-parameters. In this paper we propose a new approach that,
+based on sub-sampling and MKL, is able to speedup the parameter selection
+phase by orders of magnitude on real-world datasets  without loss in
+predictive performance.
 
@@
 In~\cite{Costa2010} the Neighborhood Subgraph Pairwise Distance Kernel (NSPDK) is presented.
-This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyperparameters $r$ and $d$, respectively).
+This kernel computes the exact matches between pairs of subgraphs with controlled size and distance (hyper-parameters $r$ and $d$, respectively).
 %The kernel has $O(|V| |V_h| |E_h| \log |E_h|)$ time complexity, where $|V_h|$ and $|E_h|$ are the number of nodes and the number of edges of the subgraph obtained by a breadth-fist visit of depth $h$.
@@
 For each baseline, the computation of all kernels is required.
-The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.
+The hyper-parameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.
 
@@
 (1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.
-In all of these methods we use a SVM as base learner. The hyperparameters sets are the same used in baselines.\\
+In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.\\
 \tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.

### 2016-11-26 paper.tex
F

@@
 computation of many large kernel matrices. In this paper we propose a method
-to efficiently select just a small number of kernels without loss in
-predictive performance.
+to efficiently select a small number of kernels on a subset of the original
+data, gaining a dramatic reduction in the runtime without a significant loss
+of predictive performance.
 
@@
 different application requires a novel feature design by some expert) and
-information loss is often unavoidable. Direct processing of structures is
-possible using a kernelized approach, where a kernel function can be devised
-for each generic data type (for example sequences, trees or graphs). This in
-turn allows to use standard learning algorithms (e.g. SVM) to solve the
-predictive task.
+information loss is often unavoidable. Instead, a direct processing of
+structures can be obtained using kernelized approaches, where a kernel
+function can be devised for each generic data type (for example sequences,
+trees or graphs). This in turn allows to use standard learning algorithms
+(e.g. SVM) to solve the desired predictive tasks.
 
-Model selection is one of the most computationally expensive tasks in a
-machine learning application. When dealing with kernel methods for structures,
+Model selection is one of the most computationally expensive tasks in
+machine learning applications. When dealing with kernel methods for structures,
 the choice with the largest impact on the overall performance is the selection
@@
 \section{Discussion and conclusion}
-In the context of MKL, we showed a procedure to learn the kernels combination vector using a subset of training data, and use this vector to chose the top kernels for a given problem.
-Then we propose three methods to combine top kernels quickly, preserving an high AUC score.
-As showed in the results table, the percentage of subsampling and top kernels selected (10\%) is a good compromise between time complexity and high AUC score.
-Furthermore, due to the low number of selected top kernels, we can assume that all of them are good kernels for our problem, so we can combine them effectively using the simple summation, avoiding to use the EasyMKL algorithms in the second learning step.\\
-Finally, our method is able to reduce effectively the time complexity, making the MKL approach usable for huge datasets.
+
+We have presented an efficient approach to model selection for graph kernels
+based on the multiple kernel learning framework. We have shown how working on
+small subsets (up to 10\%) of the data yields results that are stable and
+accurate enough to select the optimal combination of kernels via EasyMKL.
+We have investigated three methods to efficiently combine a subset of
+kernels while preserving at the same time an high AUC score for the downstream
+machine learning algorithms. Finally, we showed how we can use the simple
+summation of the selected kernels, avoiding the expensive step of running MKL
+on the full training set, to scale the MKL approach to very large
+datasets.
+
+In future work we will extend the library of graph kernels to obtain a
+comprehensive and easy to use software package.
 

### 2016-11-26 paper.tex
Typo

@@
 Each kernel in turn exposes several hyper-parameters which also need to be
-fine tuned. Finally, the downstream learning algorithm has its own hyper-
-parameters. A common approach to hyper-parameters optimization is to fix
+fine tuned. Finally, the downstream learning algorithm has its own hyper-parameters. A common approach to hyper-parameters optimization is to fix
 a-priori  a \textit{parameters grid}, i.e. a set of possible values for each
@@
 the difference between the true error and the empirical margin error).
-These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Cortes2009c}%,Hussain2011,Hussain2011a}.
+These bounds exploit the \emph{Rademacher complexity} applied to the combination of kernels \cite{Maurer2012,Cortes2009c}.%,Hussain2011,Hussain2011a}.
 %,Kakade2009,Micchelli2005,Kloft2012,Srebro2006,

### 2017-02-04 paper.tex
norma
aggiornamento figure
inserito algoritmo

@@
 
+\usepackage{color}
+
+\definecolor{mygreen}{rgb}{0,0.6,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.58,0,0.82}
+
+\usepackage{listings}
+\lstset{
+	language=Python,
+	basicstyle=\footnotesize,
+	commentstyle=\color{mygreen},
+	frame=single,
+	keepspaces=true,
+	keywordstyle=\color{blue},
+	morekeywords={*,...},
+	escapeinside={(*}{*)}, 
+	numbers=left,
+	numbersep=5pt,
+	numberstyle=\tiny\color{mygray}, 
+	rulecolor=\color{black},
+	title=Proposed algorithm	
+}
+
 % My commands
@@
 \newcommand{\XX}{{\bf X}}
+\newcommand{\XXs}{{\XX_\textsc{s}}}
 %\newcommand{\NN}{{\bf N}}
@@
 \label{eq:easymklotig}
-\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2,
+\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY \left( \sum_{r=0}^R \eta_r \KK_r\right) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2_2,
 \end{equation}
@@
 
+\begin{lstlisting}
+Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
+(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
+(*$KL_\textsc{s}$*) (*$\leftarrow$*) [ker_fun((*$\XXs$*)) for ker_fun in (*$L$*)] #calculate matrices on (*$\XXs$*)
+(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$KL_\textsc{s}$*)) #calculate weights
+(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
+(*$KL$*) (*$\leftarrow$*) [ker_fun((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #calculate top matrices on (*$\XX$*)
+\end{lstlisting}
+
 \section{Experimental Assessment}
@@
 \centering
-\includegraphics[width=0.42\textwidth]{img/CPDB_jaccard.png}
-\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}
+\includegraphics[width=0.42\textwidth]{img/CPDBh.png}
+\includegraphics[width=0.42\textwidth]{img/GDDh.png}
 \caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}

### 2017-02-06 paper.tex
modifiche parte MKL e algoritmo - ora numero pagine corretto!

@@
 MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
-The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
-$
-	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
-$
-with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space.
-The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
+The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
+$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \Psi_q = \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
 
-Using this formulation, we are studying the family of sums of kernels in the feature space.
-It is well know that the sum of two kernels can be seen as the concatenation of the features contained in both the RKHS \cite{Shawe-Taylor2004}.
-Extending the same idea, the weighted sum of a list of basic kernels can be seen as a weighted concatenation of all the features contained in all the RKHS (where the weights are the square roots of the learned weights $\eta_k$).
+Using this formulation, we are studying the family of sums of kernels in the feature space and it is well know that the sum of two kernels can be seen as the concatenation of the features contained in both the RKHS \cite{Shawe-Taylor2004}.
+Extending the same idea, the weighted sum of a list of basic kernels can be seen as a weighted concatenation of all the features contained in all the RKHS (where the weights are the square roots of the learned weights in the vector $\eeta$).
 
@@
 In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
-In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
+In particular if the combination vector learned using the whole set of data and all kernel functions $\boldsymbol{\eta}$ is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
 %In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
@@
 (*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
-(*$KL_\textsc{s}$*) (*$\leftarrow$*) [ker_fun((*$\XXs$*)) for ker_fun in (*$L$*)] #calculate matrices on (*$\XXs$*)
-(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$KL_\textsc{s}$*)) #calculate weights
+(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
+(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
 (*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
-(*$KL$*) (*$\leftarrow$*) [ker_fun((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #calculate top matrices on (*$\XX$*)
+(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
 \end{lstlisting}
@@
 datasets.
-
 In future work we will extend the library of graph kernels to obtain a

### 2017-02-06 paper.tex
rifatto algoritmo

@@
 \begin{lstlisting}
-Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
-(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
-(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
-(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
-(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
-(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
+Input: examples (*$Tr$*), list of kernel functions (*$L$*),
+kernel percentage (*$K_p$*), example percentage (*$S_p$*) 
+Output: 
+(*$S$*) (*$\leftarrow$*) random_subset_of((*$Tr, S_p$*))
+(*$K_\textsc{s}$*) (*$\leftarrow$*) [Gram(*$(S,k)$*) for k in (*$L$*)] #Gram matrices on (*$Tr_s$*)
+(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in (*$L$*)
+(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}, K_p$*)) #get the top functions
+Return [Gram((*$Tr,k$*)) for k in (*$L_{\textsc{top}}$*)] #top Gram matrices on (*$Tr$*)
 \end{lstlisting}

### 2017-02-06 paper.tex
dadam

--- 2017-02-06 paper.tex
@@
 \begin{lstlisting}
-Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
-(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
-(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
-(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
-(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
-(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
+Input: examples (*$Tr$*), list of kernel functions (*$L$*),
+kernel percentage (*$p_K$*), example percentage (*$p_S$*) 
+Output: a list of Gram matrices on (*$Tr$*)
+(*$S$*) (*$\leftarrow$*) random_subset_of((*$Tr, p_S$*))
+(*$K_\textsc{s}$*) (*$\leftarrow$*) [Gram(*$(S,k)$*) for k in (*$L$*)] #Gram matrices on (*$Tr_s$*)
+(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in (*$L$*)
+(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}, p_K$*)) #get the top functions
+Return [Gram((*$Tr,k$*)) for k in (*$L_{\textsc{top}}$*)] #top Gram matrices on (*$Tr$*)
 \end{lstlisting}

### 2017-02-06 paper.tex
Modified framework

--- 2017-02-06 paper.tex
@@
 %For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.
-
+%
 These algorithms are supported by several theoretical results that bound the \emph{estimation error} (i.e.
@@
 \section{Proposed framework}
-Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high.
+%Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high.
 Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
-In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
-In particular if the combination vector learned using the whole set of data and all kernel functions $\boldsymbol{\eta}$ is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
+%In order to avoid these problems, 
+We propose a method to reduce the number of kernels to compute on the complete dataset.
+%, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.
+We argue that the combination vector learned by EasyMKL on just a subset of the available data ($\hat{\boldsymbol{\eta}}$) is similar to the one obtained by the same algorithm on the whole dataset ($\boldsymbol{\eta}$).
+See Fig.~\ref{fig:jaccard} for an experimental assessment of this assumption.
+%In particular if the combination vector learned using the whole set of data and all kernel functions $\boldsymbol{\eta}$ is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
 %In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
-Moreover, we can use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
+We use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
 Then we compute the kernel matrix, on all the available data, for just the top kernels, and fit a model combining them.
-
+%
 %In summary, in the first phase we choose the top kernels using a subset of the available data.
 In the second phase, we calculate the top kernel matrices using the whole set of data, and then we use them in combination.
-
+A sketch of the proposed algorithm is given in the following.
+%
 \begin{lstlisting}
-Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
-(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
-(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
-(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
-(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
-(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
+Input: examples (*$Tr$*), list of kernel functions (*$L$*), 
+kernel percentage (*$p_K$*), example percentage (*$p_S$*) 
+Output: a list of Gram matrices on (*$Tr$*)
+(*$S$*) (*$\leftarrow$*) random_subset_of((*$Tr, p_S$*))
+(*$K_\textsc{s}$*) (*$\leftarrow$*) [Gram(*$(S,k)$*) for k in (*$L$*)] #Gram matrices on (*$Tr_s$*)
+(*$\hat{\boldsymbol{\eta}}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in (*$L$*)
+(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\hat{\boldsymbol{\eta}}, p_K$*)) #get the top functions
+Return [Gram((*$Tr,k$*)) for k in (*$L_{\textsc{top}}$*)] #top Gram matrices on (*$Tr$*)
 \end{lstlisting}
-
+In the algorithm, we adopted Python's list comprehension notation.
+We used the following functions:  $random\_subset\_of(tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(S,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.
 \section{Experimental Assessment}
@@
 According to preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%, except for MUTAG (the smallest datasets), where we use 20\% of training data.
-
-\begin{figure}[!htb]
+%
+%\begin{figure}[!htb]
+\begin{figure}[t]
 \centering
@@
 \end{figure}
-
+%
 To learn $\hat{\boldsymbol{\eta}}$ we chose a random subsampling of training data and perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner.

### 2017-02-07 paper.tex
tabella sistemata

@@
 In the algorithm, we adopted Python's list comprehension notation.
-We used the following functions:  $random\_subset\_of(tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(S,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.
+We used the following functions:  $random\_subset\_of(Tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(Tr,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top\_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.
 \section{Experimental Assessment}
@@
 
+%\begin{table}[]
+%\centering
+%\resizebox{\textwidth}{!}{
+%\begin{tabular}{l|c|ccc|ccc}
+%\hline\hline
+%dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
+%\hline
+%MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
+%&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
+%CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
+%&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
+%GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+%&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
+%AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+%&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
+%NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+%&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
+%NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+%&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
+%CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+%&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
+%\hline\hline
+%\end{tabular}}
+%\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
+%\label{tab:res}
+%\end{table}
+
 \begin{table}[]
@@
 \hline
-MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
+MUTAG   & 188 & \res{0.90}{0.08} & \res{0.93}{0.06} & \res{0.93}{0.06} & \res{0.93}{0.05} & \res{0.93}{0.05} & \res{0.93}{0.05}    \\
 &			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
-CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
+CPDB    & 684 & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.02} & \res{0.89}{0.03} 	& \res{0.88}{0.02} \\
 &			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
-GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
+GDD     & 1178 & \res{0.86}{0.05} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.80}{0.04}    \\
 &			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
-AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
+AIDS    & 1503 & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.77}{0.07} & \res{0.77}{0.07}    \\
 &		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
-NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
+NCI1    & 4110 & \res{0.88}{0.04} & - & \res{0.89}{0.04} & \res{0.88}{0.04} & \res{0.88}{0.05} & \res{0.88}{0.04}    \\
 &	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
-NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
+NCI109 & 4127 & \res{0.87}{0.03} & - & \res{0.87}{0.03} & \res{0.87}{0.02}  & \res{0.87}{0.03} & \res{0.87}{0.02}  \\
 &	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
-CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
+CAS     & 4337 & \res{0.92}{0.01} & - & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01}    \\
 &	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h

### 2017-02-08 paper.tex
6 pages again!

@@
 	rulecolor=\color{black},
-	title=Proposed algorithm	
+	%title=Proposed algorithm	
 }
@@
 %and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.
-
+%
+%
 \section{Proposed framework}
@@
 The hyper-parameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.
+%
 
@@
 (1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.
-In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.\\
+In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.
 \tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.
-
+%
 %\begin{table}[]
@@
 %\end{table}
-
-\begin{table}[]
+%
+%
+\begin{table}[t]
 \centering
+\small
 \resizebox{\textwidth}{!}{
@@
 \end{table}
-
+%
 \section{Discussion and conclusion} 
-
+%
 We have presented an efficient approach to model selection for graph kernels
@@
 % ****************************************************************************
-
+%
 \begin{footnotesize}
-
+%
 % IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
@@
 % - UNCOMMENT THE NEXT TWO LINES AND REPLACE 'Name_Of_Your_BibFile'
-
+%
 \bibliographystyle{unsrt}
 \bibliography{donini,biblio,Mendeley}
-
+%
 \end{footnotesize}
-
+%
 % ****************************************************************************

### 2017-02-08 paper.tex
piccola correzione MKL
caratteristiche cpu inserite
compressione

@@
 The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
-$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \Psi_q = \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
+$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
 
@@
 We used the following functions:  $random\_subset\_of(Tr,p_S)$  samples a percentage $p_S$ of the examples in the set $Tr$; $Gram(Tr,k)$ computes the \textit{Gram} matrix of the kernel $k$ on the set of examples $Tr$; \textit{EasyMKL($K_s$)} computes a list of weights (one for each kernel in $K_s$) according to the EasyMKL algorithm; $top\_of(L,\hat{\boldsymbol{\eta}},p_K)$ extracts the top $p_K$ percentage of the elements in $L$ according to the weights $\hat{\boldsymbol{\eta}}$.
+\vspace{-0.5cm}
 \section{Experimental Assessment}
@@
 In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.
-\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.
+\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time.\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}
+ used to make kernels and models for all problems.
 %
@@
 %
+\vspace{-0.15cm}
 \section{Discussion and conclusion} 
@@
 %
+\vspace{-0.2cm}
 \begin{footnotesize}

### 2017-02-08 paper.tex
piccole correzioni

@@
 In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.
-\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time.\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}
+\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}.
  used to make kernels and models for all problems.

### 2017-02-08 paper.tex
correzioni varie

@@
 \label{MKL}
-MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
-The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
+MKL \cite{Gonen2011} is one of the most popular paradigms in real world applications \cite{Bucak2014} used to learn kernels as a combination of different base kernels $\KK_1,...,\KK_R$.
+% Zien2007,Wang2015a,Sun
+In literature exists several kernels combination mechanisms, we focused on the form:
 $ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
